### 2023-09-24 README.Rmd
Updated description, added DOI to Zenodo repository

# se.norway.shoredate.14c

@@

> Roalkvam, Isak <a href="https://orcid.org/0000-0001-6974-1374"> <img alt="ORCID logo" src="https://info.orcid.org/wp-content/uploads/2019/11/orcid_16x16.png" width="16" height="16" /></a> and Solheim, Steinar <a href="https://orcid.org/0000-0001-8293-8147"> <img alt="ORCID logo" src="https://info.orcid.org/wp-content/uploads/2019/11/orcid_16x16.png" width="16" height="16" /></a> (2023). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Roalkvam, Isak and Solheim, Steinar (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.

>>>>

# Comparing summed probability distributions of shoreline and radiocarbon dates from the Mesolithic Skagerrak coast of Norway

@@

> Roalkvam, Isak <a href="https://orcid.org/0000-0001-6974-1374"> <img alt="ORCID logo" src="https://info.orcid.org/wp-content/uploads/2019/11/orcid_16x16.png" width="16" height="16" /></a> and Solheim, Steinar <a href="https://orcid.org/0000-0001-8293-8147"> <img alt="ORCID logo" src="https://info.orcid.org/wp-content/uploads/2019/11/orcid_16x16.png" width="16" height="16" /></a> (2023). _`r Title`_. Online at <https://doi.org/xxx/xxx>

@@

> Roalkvam, Isak <a href="https://orcid.org/0000-0001-6974-1374"> <img alt="ORCID logo" src="https://info.orcid.org/wp-content/uploads/2019/11/orcid_16x16.png" width="16" height="16" /></a> and Solheim, Steinar <a href="https://orcid.org/0000-0001-8293-8147"> <img alt="ORCID logo" src="https://info.orcid.org/wp-content/uploads/2019/11/orcid_16x16.png" width="16" height="16" /></a> (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.8373857>

@@

The **R** directory contains scripts for performing the analyses and create the
figures used in the paper.

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. It also has a rendered version of the manuscript,
    `paper.pdf`, suitable for reading.
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
